### 2020-05-21 preface.tex
Shorten preface to fit on one page

The conference had 224 participants, and 188 papers were presented. These high numbers are a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field of argumentation. The contents of these three volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.

>>>>

ECA 2019 had 224 participants and 188 paper presentations, a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field. These three volumes reflect the current state of the art in argumentation scholarship in general.
